---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
  knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

```{r, include = FALSE}
## Build the README by running `devtools::build_readme()`
```

# Spectrum regression testing

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

This is a shiny app and package for comparing different runs of AIM via extract.

## Installation

You can install the development version of `{spectrum.regression.testing}` like so:

```{r, eval = FALSE}
remotes::install_github("AvenirHealth-org/spectrum.regression.testing")
```

## Setup

This app uses data from 2 different sources

1. Dropbox
2. spectrum-orderly

To use dropbox data, we need to provide a path to the locally synced or downloaded extract files. Run the `./scripts/initialize_data.R` to help setup this environment. It will prompt you for a path to the "extracts" directory which contains output from running the Spectrum extract tool. Files will then be read from this directory.

TODO: Fill in details of working with the different data

## Run

You can launch the application by running:

```{r, eval = FALSE}
spectrum.regression.testing::run_app()
```

To run in development run the script `./scripts/run_dev.R` or source the app in an R session with `devtools::load_all()` and then run the app with `run_app()`
